There are many free Apps for both PC and Android to diagnose your car via OBD2 port.
These Apps give access to data such as fault codes, current rpm, oil temperature and many more.
Since older cars don't have fancy touch screens it would make sense to have some app running and reading this data to show out on screen.

To have more general statistics for a driver it would make sense to sync them up to some database so that you could access the data also outside your car.
This would also give the possibility to see stats containing many cars and compare different car marks / models stats to one another.


\section{Project scope}\label{sec:project-scope}
The scope of this project is to build web application and database system capable of storing and querying data from multiple users at once.
Building an app capable of reading desired data from a car is not in the scope of this project and will be done at a later time.
Although there will be no actual client to upload data, proper API endpoints shall still be made.
During the course, possibly android app made last year will be used to get mock data.

\textbf{Must haves:}
\begin{itemize}
    \item ERD schema.
    \item Controllers for desired CRUD operations with entities.
    \item Views for Refills, tracks and statistics.
    \item Detailed view for a track.
    \item Server must be scalable to allow numerous clients.
    \item Api endpoints must be secured.
\end{itemize}

\textbf{Nice to haves:}
\begin{itemize}
    \item Comparison mode for statistics (car vs type average etc.).
    \item Live data for tracks.
    \item Heatmaps.
\end{itemize}